---
title: "Panel Data Creater"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
R code for creating panel data sets.

## Motivation

Panel data sets are tricky because most data sets we find are either excel sheet format arranged by year or documents that needs to be manually arranged so that it can be prepared for analysis.

This is a simple R code that helps turning a single .xlsx file with multiple year-sheets to a panel data set.

## Code

### Single File With Year .xlsx Sheets


```{r eval=FALSE}
# Panel Data Creater

# Libraries

library(readxl)
library(foreign)

# Set Directory
setwd(#directory)

filename<-#file.xlsx
column_name<-#vector of column names, without 'year' 

# Function that Reads a Sheet
read_f<-function(i) {
  df<-read_xlsx(filename, sheet = i, col_names = TRUE)
  colnames(df)<-column_names
  return(df)
}

# Loop the Function Over Multiple Sheets, Store Sheet Results in List

n = #maximum number of sheets to loop 
year_vector = #a vector of years
  
get_datalist<-function() {
  datalist = list()
  for (i in 1:n) {
    df<-read_f(i)
    # while looping, add 'year' to the column
    years = year_vector
    df$year<-years[i]
    datalist[[i]]<-df
  }
  return(datalist)
}

# Row Bind Elements in the List

panel_data<-do.call(rbind,get_datalist())

# Save Results as .RData
output_filename = #output_filename.rda
save(panel_data,file=output_filename)

# Save Results as .dta for STATA
output_filename2 = #output_filename.dta
write.dta(panel_data,file=output_filename2)
```

### Example

This is an example of usage of the code above on a .xlsx sheet containing sheets across 1993-2007 period on number of public employees and other indicators across provinces in China.

```{r warning=FALSE}
# Libraries

library(readxl)
library(foreign)

# Set Directory
setwd("~/Dropbox/Data_Insert/Final_Version")

filename<-"Final_Edited_1116.xlsx"
column_names<-c("id","province_name","population","rural_population","public_employees",
                  "profit_making_pe","local_gr","local_ex","total_ex",
                  "gdp_nat","farming_output")

# Function that Reads a Sheet
read_f<-function(i) {
  df<-read_xlsx(filename, sheet = i, col_names = TRUE)
  colnames(df)<-column_names
  return(df)
}

# Loop the Function Over Multiple Sheets, Store Sheet Results in List

n = 15 
year_vector = c(1993:2007)
  
get_datalist<-function() {
  datalist = list()
  for (i in 1:n) {
    df<-read_f(i)
    # while looping, add 'year' to the column
    years = year_vector
    df$year<-years[i]
    datalist[[i]]<-df
  }
  return(datalist)
}

# Row Bind Elements in the List

panel_data<-do.call(rbind,get_datalist())
panel_data<-as.data.frame(panel_data)

head(panel_data)
```

